---
title: "Vignette of the a4Preproc package"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float:
      collapsed: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{a4Preproc package}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Introduction

This document explains the functionalities available in the
**a4Preproc** package.


This package contains utility functions to pre-process data for the Automated Affymetrix Array Analysis 
suite of packages.

```{r loadLibraries, results = 'hide', echo = FALSE}

	library(a4Preproc)

```

# Get feature annotation for an ExpressionSet

The feature annotation for a specific dataset, as required by the pipeline
is extracted with the `addGeneInfo` function.

```{r addGeneInfo, message = FALSE}
library(ALL)
data(ALL)
a4ALL <- addGeneInfo(eset = ALL)
print(head(fData(a4ALL)))
print(head(featureData(a4ALL)))
```

# Appendix

## Session information

```{r sessionInformation, echo = FALSE}
print(sessionInfo())
```